Proportional multi-state multiple-cohort life table model

### 2018-04-13 MSLT/MSLTdoc.Rmd
Loop graphs

sex <- c("male", "female")
cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancers", "breast cancer", "tracheal, bronchus, and lung cancer")
measure <- c("all causes", "ylds (years lived with disability)", "prevalence", "incidence")

for (i in sex){
  for (j in cause) {
    for (k in measure) {
      p <- paste("Plot", "compare", sex, cause, measure, sep = "_")
      assign(p, plot_GBD(in_data1 = GBDEngland, in_data2 = GBDGL, in_sex = sex, in_cause = cause, in_measure = measure))
      print(p)
    }
  }
}

>>>>

p_sex <- c("male", "female")
p_cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancers", "breast cancer", "tracheal, bronchus, and lung cancer")
p_measure <- c("all causes", "ylds (years lived with disability)", "prevalence", "incidence")

for (sex in p_sex){
  for (cause in p_cause) {
    for (measure in p_measure) {
      p1 <- plot_GBD(in_data1 = GBDEngland, in_data2 = GBDGL, in_sex = sex, in_cause = cause, in_measure = measure)
      dev.new()
      print(p1)

    }
  }
}
